---
title: "Data Science Methods, Lab X: Title"
author: "Your Name"
output:
  html_document:
    toc: true
---
# Introduction #


# Reflexivity #

Before starting the lab, spend 5 minutes writing a response to each reflexivity question.  Use a timer.  Answer these questions off the top of your head: don't worry about consulting or citing outside sources or about getting the answers "right" or "wrong." 
(Adapted from Tanweer et al., "Why the Data Revolution Needs Qualititative Thinking," <https://doi.org/10.1162/99608f92.eee0b0da>, and Liboiron, _Pollution is Colonialism_, <https://www.dukeupress.edu/pollution-is-colonialism>.) 

1. What do I already know about this subject? 
2. Why am I studying this? 
3. What do I expect or hope to find/learn, and why? 
4. Who is affected by this topic, and how am I connected to them? 


# Setup #
**IMPORTANT**: Add all dependencies to `DESCRIPTION`

```{r}

```


```{r}
## To check your answers locally, run the following: 
## testthat::test_dir('tests')
```

# Problem 1 #

1. Assign the value `2L` to `foo`.

```{r}
foo = 2L
```

